---
title: "HW_02_Stat_RStudio"
author: "Lilit Hovsepyan"
date: "28 09 2019"
output: html_document
---
Problem 1.  
c. Simulate 100 Die Roll.
1) Frequency Table
2) ECDF
3) BarPlot

```{r}
# 1.Frequency table
res <- c(sample(1:6, 100, replace = T))
y <- table(res)
y
```


```{r}
# 2.ECDF
res <- c(sample(1:6, 100, replace = T))
f <- ecdf(res)
plot(f)
```

```{r}
# 3.BarPlot
barplot(table(res))
```
d. Check that ECDF approximates well the CDF behind the data.
1) Generate 1000 samples from the Exp(0.3) distribution
2) Plot the ECDF of the result
3) Plot over the previous graph the theoretical CDF of the distribution, with green color and linewidth 2 (use the lwd=2 parameter value in plot)

```{r}
# 1.Gen. the 1000 samples from the Exp(0.3) dist.
y<-rexp(1000,rate = 0.3)
head (y)
```

```{r}
# 2.Plot the ECDF of the result.
yy<-ecdf(y)
plot(yy, xlim=c(0,25), ylim=c(0,1))
```

```{r}
# 3.Plot over the previous graph the theoretical CDF.
yy<-ecdf(y)
plot(yy, xlim=c(0,25), ylim=c(0,1))
par(new=T)
range = seq(0,25,0.1)
plot(range, pexp(range, rate = 0.3), lwd = 2, col = "green", xlim=c(0,30), ylim=c(0,1), type="l", ylab = " ", xlab = " ")
# curve(density(y),add=T, col="green", lwd="3")
```

Problem 2.

b. Consider one of the standard Datasets in R, islands.

1) Call the help page for this Dataset to see the description,
2) Print the structure of the Dataset,
3) Print the head of this Dataset,
4) Plot the Frequency Histogram for the islands with the area less than 200 sq miles,
5) Plot the Density Histogram for the islands with the area less than 200 sq miles,
6) Add to the previous plot the KDE (in red, with linewidth 3) for the islands with the area less than 200 sq miles

```{r}
# 1.Call the help page for this Dataset to see the description.
help(islands)
```

```{r}
# 2.Print the structure of the Dataset.
structure(islands)
```
```{r}
# 3.Print the head of this Dataset.
head(islands)
```
```{r}
# 4.plot the Frequency Histogram for the islands with the area less than 200 sq miles.
islands[islands<200]
hist(islands[islands<200])
```
```{r}
# 5.plot the Density Histogram for the islands with the area less than 200 sq miles.
islands[islands<200]
hist(freq=F, islands[islands<200])
```
```{r}
# 6.Add to the previous plot the KDE (in red, with linewidth 3) for the islands with the
hist(freq=F, islands[islands<200], ylim = c(0,0.02), las=1)
par(new=T)
kde<-density(islands[islands<200])
plot(kde, col="red", lwd=3, main="", ylab = "", xlab = "", xlim=c(0,200), las=1, ylim=c(0,0.02))
```

c. Here we want to check that the Density Histogram is approximating well the PDF behind the data. To that end, we consider the Weibull distribution

1) Take n = 1000
2) Generate a sample of size n from the Weibull distribution with the  shape parameter 2
3) Plot the Density Histogram of that sample, in cyan color
4) Plot the theoretical PDF (use dweibull in R) over the previous graph, in red, and with linewidth 3

```{r}
# 1.- 4.
n<-1000
x <- rweibull(n,2,1)
d <- density(x)
hist(x, freq = F, xlim = c(0,5), ylim = c(0,1), col = "cyan", main = " ")
rug(x)
par(new=T)
plot(d, lwd = 3, col = "red", xlim = c(0,5), ylim = c(0,1), main = " ", xlab = " ")

```
d. Now let’s plot compatarive Histograms. We will work with the R-s default ChickWeight Dataset.

1) Explore the Dataset: read the description and print the first 5 rows of that Dataset
2) Separate in x the Weight variable for all Chicken with the Diet 1
3) Separate in y the Weight variable for all Chicken with the Diet 2
4) Plot the Frequency Histograms of x and y one over another.

```{r}
# 1. Explore the Dataset: read the description and print the first 5 rows of that Dataset
help(ChickWeight)
head(ChickWeight,5)
```

```{r}
# 2. Separate in x the Weight variable for all Chicken with the Diet 1
x<-ChickWeight$weight[ChickWeight$Diet==1]
head(x)
```

```{r}
# 3. Separate in y the Weight variable for all Chicken with the Diet 1
y<-ChickWeight$weight[ChickWeight$Diet==2]
head(y)
```

```{r}
# 4. Plot the Frequency Histograms of x and y one over another
library(scales)
hist(x, col=alpha("magenta",0.2), las=1, ylim = c(0,80), xlab = " ", main = " ")
par(new=T)
hist(y, col=alpha("green",0.5), las=1, ylim = c(0,80), xlab = "x and y", main = "Histogram of x and y")
```

Problem 3.

c. Consider the iris Dataset.

1) Choose the Petal.Length variable and make its S-n-L Plot
2) Now do the same variable S-n-L Plot with the scale parameters = to 0.5, 2 and 4
3) (Supplementary) Now plot the S-n-L Plot and Histogram of our Dataset side-by-side.

```{r}
# 1. Choose the Petal.Length variable and make its S-n-L Plot
a<-iris$Petal.Length
stem(a)
```

```{r}
# 2. Now do the same variable S-n-L Plot with the scale parameters = to 0.5, 2 and 4
a<-iris$Petal.Length
stem(a, scale=0.5)
stem(a, scale=2)
stem(a, scale=4)
```
```{r}
# 3. Now plot the S-n-L Plot and Histogram of our Dataset side-by-side.
par(mfcol=c(1,2))
hist(a)
a <-iris$Petal.Length
plot.new()
out <- capture.output(stem(a))
text(0,1,paste(out, collapse = '\n'), adj=c(0,1), family='mono')
```
Problem 4.

a. Plot the following points:
(0, 2), (3,-1), (4, 2), (5, 5), (-1, 2)

b. R-s pressure Dataset consists of 2 Variables. Give the ScatterPlot of these Variables.

```{r}
# a. 
x<-c(0,3,4,5,-1)
y<-c(2,-1,2,5,2)
plot(x,y)
```
```{r}
# b. 
help(pressure)
x<-pressure$temperature
y<-pressure$pressure
plot(x,y)
```

Problem 5.

```{r}
aapl<-read.csv(file.choose())
Adj_close <- aapl$Adj.Close
head(aapl)
r<-(Adj_close[2:length(Adj_close)]-Adj_close[-length(Adj_close)])/Adj_close[-length(Adj_close)]
head(r)
hist(r)
```
Here we see that the returns are almost closer to 0 both form the left and from the right sides. And most of the datapoints are in the center.

Problem 6.

f. ChickWeight Dataset from R.

1) Calculate the Mean of Wights for chicken fed with the first diet
2) Calculate the Mean of Wights for chicken fed with the second diet
3) Compare the results: can the difference between the means be the result of just randomness, or we can state that one of the diets is better than the other one?

```{r}
# 1. Calculate the Mean of Wights for chicken fed with the first diet
w1<-ChickWeight$weight[ChickWeight$Diet==1]
mean(w1)
```
```{r}
# 2. Calculate the Mean of Wights for chicken fed with the second diet
w2<-ChickWeight$weight[ChickWeight$Diet==2]
mean(w2)
122.6167-102.6455
```
 3) Compare the results: can the difference between the means be the result of just randomness, or we can state that one of the diets is better than the other one?
 Here we see that the chicken mean weight in case of the first type of experimental diet is 102.6455, for the second type it is higher by 19.9712. Maybe the second type of diet was better than the first one, and on average chicks started to get higher weight.

Problem 7.

d. Calculate and compare the Sample Standard Deviations and Variances for the mpg variable from the Dataset mtcars for different cylinder type cars. For example, compare 6 cylinder cars mpg-s SD with the 4 cylinder cars mpg-s SD.

```{r}
a <- mtcars$mpg[which(mtcars$cyl==6)]
var(a)
sd(a)

b <- mtcars$mpg[which(mtcars$cyl==4)]
var(b)
sd(b)

sd(b)-sd(a)
```

e. We consider the iris Dataset. For which type of the flower (for which Species) the variability in Petal.Width is maximal, and for which is minimal.

```{r}
x <- iris$Petal.Width
y <- x[which(var(x) == max(var(x)))]
iris$Species[which(iris$species == y)]
z <- x[which(var(x) == min(var(x)))]
iris$Species[which(iris$species == z)]
```

f.1) Calculate the Median Absolute Deviation from the Median for the dist variable of the cars Dataset

```{r}
mad(cars$dist)
```

f.2) Calculate the Median Absolute Deviation from the Mean for the dist variable of the cars Dataset.
```{r}
mad(cars$dist, center = mean(cars$dist))
```
f.3) Write a function mad1 which will calculate the Mean Absolute Deviation from the
Mean.

```{r}
y <- cars$dist - mean(cars$dist)
mad1 <- mean(abs(y))
mad1
```

f.4) Write a function mad2 which will calculate the Mean Absolute Deviation from the
Median.

```{r}
x <- cars$dist - median(cars$dist)
mad2 <- mean(abs(x))
mad2
```


Problem 8

c.
1) Calculate the Quartiles of x and y form part a. by using the quantile function.

```{r}
# 1. Calculate the Quartiles of x and y form part a. by using the quantile function.
x <- c(-6, 15, 0, 5, 17, -4, 1, -9, -9, 13)
y <- c(0.0, 3.6, 2.7, -1.5, 5.7, 1.5, -3.0, 4.5, 6.0)

q1_x<-quantile(x, 0.25)
q2_x<-median(x)
q3_x<-quantile(x, 0.75)
q1_x
q2_x
q3_x

q1_y<-quantile(y, 0.25)
q2_y<-median(y)
q3_y<-quantile(y, 0.75)
q1_y
q2_y
q3_y
```
2) Write an R function quartile(x) which will return the Quartiles of the input vector x just like we have defined.
```{r}
quartile <- function(x){
  q2 <- median(x)
  q1 <- median(x[which(x<=q2)])
  q3 <- median(x[which(x>=q2)])
  q <- c(q1, q2, q3)
  return(q)
}

quartile(x)
```



